% !TEX encoding = UTF-8 Unicode
%!TEX root = ../Main/thesis.tex
% !TEX spellcheck = en-US
%%=========================================
\documentclass[../Main/thesis.tex]{subfiles}
\begin{document}
\chapter{System Usability Scale}
\label{app:sus}
\section{SUS Questions}
\begin{enumerate}
	\item I think that I would like to use this system frequently.
	\item I found the system unnecessarily complex.
	\item I thought the system was easy to use.
	\item I think that I would need the support of a technical person to be able to use this system.
	\item I found the various functions in this system were well integrated.
	\item I thought there was too much inconsistency in this system.
	\item I would imagine that most people would learn to use this system very quickly.
	\item I found the system very cumbersome to use.
	\item I felt very confident using the system.
	\item I needed to learn a lot of things before I could get going with this system.
\end{enumerate}

\newpage

\section{Norwegian Translation of SUS Questions}
\begin{enumerate}
	\item Jeg tror at jeg ville ha brukt dette systemet ofte.
	\item Jeg synes at systemet var unødvendig vanskelig.
	\item Jeg synes systemet var enkelt å bruke.
	\item Jeg tror at jeg ville ha trengt støtte fra en teknisk person i bruken av dette systemet.
	\item Jeg synes at funksjonene i systemet var godt integrerte.
	\item Jeg synes systemet var lite konsekvent.
	\item Jeg tror at de fleste ville ha lært seg å bruke systemet veldig fort.
	\item Jeg synes systemet var veldig tungvint å bruke.
	\item Jeg følte meg selvsikker i bruken av systemet.
	\item Jeg måtte ha lært meg mange ting før jeg kunne ha tatt systemet skikkelig i bruk.
\end{enumerate}

\end{document}
